Final Report

### 2022-05-06 Final Report.Rmd
changed colnames to rename

---
title: "Final Report"
author: "Alison Cheek & Elizabeth Bekele"
date: '2022-05-06'
output: html_document
---

>>>>

---
title: "Final Report"
author: "Alison Cheek & Elizabeth Bekele"
date: '2022-05-06'
output: html_document
---
We were excited to do our report over this data because it was relatively tidy and had quite a few categorical variables and options for additional columns to graph.
